Titeln på avhandlingens språk

### 2023-01-28 body/part1/background.tex
editing

However, the cloud is not suitable for all applications, and presents important drawbacks and challenges for bandwidth-hungry, privacy-requiring, and/or latency-sensitive applications.
Current cloud infrastructures are ill-suited to deal with the tremendous amounts of data generated by \gls{IOT} sensor networks.
The centralized nature of cloud data centers, which are often placed a large distance away from potential users, lead to prohibitively high latencies for highly interactive immersive applications such as mobile \gls{XR}\citationeeded.
Furthermore, this same centralized nature has led to concerns about the security of cloud computing\todo{needs to be expanded a bit}.

Edge computing emerges as an answer to these challenges~\cite{satyanarayanan2009case,satyanarayanan2017emergence}.
This term refers to a novel distributed computing paradigm, complementary to cloud computing, which tackles the challenges of the cloud by moving computation closer to where it is needed.
Instead of offloading computation to a datacenter potentially thousands of kilometers away, in edge computing it is offloaded to a micro-datacenter --- a \emph{cloudlet}~\cite{satyanarayanan2009case} --- at the \emph{edge} of the network, one or two hops away from the user.
This design leads to several advantages.
One, edge computing is uniquely suited for highly latency-sensitive yet resource-intensive applications such as the aforementioned mobile \gls{XR} as well as \gls{CPS}~\cite{sasaki2016vehicle,wang2018bandwidth,wan2020efficient}.

>>>>

However, the cloud is not suitable for all applications, and presents important drawbacks and challenges for bandwidth-hungry, privacy-requiring, and/or latency-sensitive applications.
Current cloud infrastructures are ill-suited to deal with the tremendous amounts of data generated by \gls{IOT} sensor networks~\cite{shi2016edge}.
The centralized nature of cloud data centers, which are often placed a large distance away from potential users, lead to prohibitively high latencies for highly interactive immersive applications such as mobile \gls{XR}~\cite{satyanarayanan2009case,varghese2016challenges,shi2016promise}.
Furthermore, this same centralized nature has led to concerns about the security of cloud computing\todo{needs to be expanded a bit}.

Edge computing emerges as an answer to these challenges~\cite{satyanarayanan2009case,shi2016promise,shi2016edge,varghese2016challenges,satyanarayanan2017emergence}.
This term refers to a novel distributed computing paradigm, complementary to cloud computing, which tackles the challenges of the cloud by moving computation closer to where it is needed.
Instead of offloading computation to a datacenter potentially thousands of kilometers away, in edge computing it is offloaded to a micro-datacenter --- a \emph{cloudlet}~\cite{satyanarayanan2009case} --- at the \emph{edge} of the network, one or two hops away from the user.
This design leads to several advantages.
One, edge computing is uniquely suited for highly latency-sensitive yet resource-intensive applications such as the aforementioned mobile \gls{XR} as well as \gls{CPS}~\cite{sasaki2016vehicle,wang2018bandwidth,wan2020efficient}.

\todo[inline]{Include diagram edge versus fog versus cloud.}
